---
title: "targeted_ICC_validation"
author: "Yoo Ri Hwang"
date: "4/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##packages
```{r}

library(tidyverse)
library(MASS)
library(jtools) #to get nicer output
library(lme4)
library(lmerTest)

library(multilevel)
library(nlme)
library(simstudy)
library(rlist)
library(readxl)
```

## function

```{r, eval=FALSE}


# Data generation function (dyad structure)
source('scripts/gen_dyadic.R')
source('scripts/gen_rmvn.R')

# function to convert dyad structure into dyad2individual structure
source('scripts/dyad_to_long.R')

# the function for sibling comparison model
source('scripts/model_sib.R')

# the function for null model
source('scripts/model_null.R')

# the function for mlm model
source('scripts/model_mlm.R')

# the function for ICC weight calculator
source('scripts/ICC_calculator.R')


```

## Vaildation
### check the ICC for generated data (per condition)

```{r}

conditions<-read.csv(file='ICC_calculator_validation/ICC_Conditions.csv')
# conditions$ID <- 1:36
# conditions$wtn <- 100  # within ICC weights 
# 
# 
# # creat a loop
# conditions <- as.data.frame(conditions)
# 
# for(i in 1:36){
#  conditions$btw[i]<-ICC_calculator( 
#    
#    beta1 = conditions$beta1[i],
#    beta2 = conditions$beta2[i],
#    beta3 = conditions$beta3[i],
#    ICC = conditions$targeted_ICC[i],
#    within= conditions$wtn[i]
#  )
# }
# 
# write.csv(conditions, file='ICC_calculator_validation/ICC_Conditions.csv')

```

```{r}


nrep <- 999
sim_result <- vector ("list", length = nrep)
icc <- vector("list", length=nrep)


for( i in 1:36){

    sim_dat <- gen_dyadic(
    cn= 510,
    beta1 = conditions$beta1[i],
    beta2 = conditions$beta2[i],
    beta3 = conditions$beta3[i],
    con_icc_wtn = conditions$wtn[i],
    con_icc_btw = conditions$btw[i],
    cat_icc_wtn = conditions$wtn[i],
    cat_icc_btw = conditions$btw[i])

  sim_dat <- dyad2ind(sim_dat)
  null <- model_null(df=sim_dat)

  for (k in  seq_len(nrep)) {
   # run a null model

  sim_result[[k]] <- jtools::summ(null) # put nicer output in the list
   icc[[k]]<-unlist(sim_result[[k]][3])[3] #extract ICC

  }
   df <- data.frame(matrix(unlist(icc), nrow=length(icc), byrow=TRUE))
  colnames(df) <- c('icc')
  df$icc2 <-as.numeric(df$icc)
  # mean of these icc CHECK
  meanICC <- mean(df$icc2)

  conditions$real_ICC[i] <- meanICC
}



```

```{r, eval=FALSE}
# nrep<-999
# sim_result <- vector ("list", length = nrep)
# 
# icc <- vector("list", length=nrep)
# for(k in 1:36)
# for (i in seq_len(nrep)) {
#   sim_dat <- gen_dyadic(cn=510,
#   con_icc_wtn = 100,
#   con_icc_btw = 17.5,
#   cat_icc_wtn = 100,
#   cat_icc_btw = 17.5,
#   beta1 = 0.3,
#   beta2 = 0.1,
#   beta3 = 0) # generate data 
#   sim_dat <- dyad2ind(sim_dat) # convert dyadic structure into dyad2individual structure 
#   null <- lmer(y~1+(1|pid), data=sim_dat) # run a null model 
#   sim_result[[i]] <- jtools::summ(null) # put nicer output in the list 
#    icc[[i]]<-unlist(sim_result[[i]][3])[3] #extract ICC 
# }
# 
# # Make a nicer output for it
# 
#   df <- data.frame(matrix(unlist(icc), nrow=length(icc), byrow=TRUE))
#   # Change column names
#   colnames(df) <- c('icc')
#   df$icc2 <-as.numeric(df$icc)
#   # mean of these icc CHECK
#   meanICC <- mean(df$icc2)
#   
#   # visualize CHECK
#   graph<-
#     df %>%
#     ggplot(aes(x=icc2)) +
#     geom_density()
#   
# 
# 

```


# example: 

##   data1

ICC = 0.2 
Cluster size= 30
beta1= 0.3
beta2= 0.1 
beta3= 0.1 

## data generation 
```{r}

data1 <- gen_dyadic(
  cn=30,
  con_icc_wtn = 34,
  con_icc_btw = 1,
  cat_icc_wtn = 34,
  cat_icc_btw = 1,
  beta1 = 0.3,
  beta2 = 0.1,
  beta3 = 0.1
)

```
## checking ICC 

due to the small cn (cluster number)
it throws error message :
boundary (singular) fit: see ?isSingular

```{r}


 # number of replication
# make empty list (place holder)
 
  # creat a loop

nrep<-999

sim_result <- vector ("list", length = nrep)

icc <- vector("list", length=nrep)

for (i in seq_len(nrep)) {
  sim_dat <- gen_dyadic(cn=510,
  con_icc_wtn = 100,
  con_icc_btw = 230,
  cat_icc_wtn = 100,
  cat_icc_btw = 230,
  beta1 = 0.3,
  beta2 = 0.1,
  beta3 = 0.5) # generate data
  
  sim_dat <- dyad2ind(sim_dat) 
  # convert dyadic structure into dyad2individual structure 
  null <- lmer(y~1+(1|pid), data=sim_dat) # run a null model 
  sim_result[[i]] <- jtools::summ(null) # put nicer output in the list 
   icc[[i]]<-unlist(sim_result[[i]][3])[3] }#extract ICC 
   
  df <- data.frame(matrix(unlist(icc), nrow=length(icc), byrow=TRUE))
   colnames(df) <- c('icc')
  df$icc2 <-as.numeric(df$icc)
  meanICC <- mean(df$icc2)
  meanICC 


# Make a nicer output for it

  df <- data.frame(matrix(unlist(icc), nrow=length(icc), byrow=TRUE))
  # Change column names
  colnames(df) <- c('icc')
  df$icc2 <-as.numeric(df$icc)
  # mean of these icc CHECK
  meanICC <- mean(df$icc2)
  
  # visualize CHECK
  graph<-
    df %>%
    ggplot(aes(x=icc2)) +
    geom_density()
  
  ## 
  graph
  meanICC
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
