---
title: "ICC_interaction"
author: "Yoo Ri Hwang"
date: "4/22/2022"
output: html_document
---
For future yoori who wants to extend the master thesis.


This project contains how to manipulate ICC whe interaction is
within level (genderwitnint *edu within)
between level (genderbetween*edubetween)
full((genderwith+genderbetween)*(eduwithin+edubetween))
human level (gender within * edu whole )


between*between interaction = between = dyad pair shares the same value
within *within interaction term = within  = this is independent among two members.4

Yoo Ri's conjecture. ♦

between*within interaction
= the covariance of this variable : between
= the left ovef of this variable : within 

```{r}


library(MASS)
library(tidyverse)
library(lme4)
```

```{r}



gen_dyadic <- function(full=FALSE,
                       researcher=FALSE, # true releases only what the researcher would have (human being's eye)
                       cn=120, # what is this?
                       con_mu=c(0,0,0,0), #mean
                       con_vcovmatrix=matrix(c(1,0,0,0,
                                            0,1,0,1,
                                            0,0,1,0,
                                            0,1,0,1),
                                          nrow = 4,
                                          byrow = TRUE,
                                          dimnames = list(c("con_wtn_1","con_btw_1","con_wtn_2","con_btw_2"),
                                                          c("con_wtn_1","con_btw_1","con_wtn_2","con_btw_2"))),
                      con_icc_wtn = .3,
                      con_icc_btw = .7,
                      cat_icc_wtn = .3,
                      cat_icc_btw = .7, # if con/cat things are different, it may cuase some problem in interaction
                      beta1 = .3, #beta weight for continuous variable on individual regression
                      beta2 = .3, #beta weight for the categorical variable on individual regression
                      beta3 = 0 # beta weight for interaction

){
  ## adjusting between and within variance in continuous variable
require(MASS)
require(tidyverse)



  ## Continuous variable
  dat <- MASS::mvrnorm(cn, # cluster  number
                       mu = con_mu, # Mu
                       Sigma = con_vcovmatrix) %>% # Covariance matrix
    as.data.frame() %>%
    mutate(
      pid = 1:cn, ## id column
      con_1 = sqrt(con_icc_wtn) * con_wtn_1 + sqrt(con_icc_btw) * con_btw_1,
      con_2 = sqrt(con_icc_wtn) * con_wtn_2 + sqrt(con_icc_btw) * con_btw_2,
      ## categorical within
      catwtn_1 = sample(rep(c(-1, 1), cn / 2)),
      catwtn_2 = sample(rep(c(-1, 1), cn / 2)),
      ## categorical between -- we are assumed that mixed sex sibing is beneficial to the health, compared to the
      ## same-sex siblign. this shold be addressed in limitation.
      catbtw_1 = case_when(
        catwtn_1 == 1 & catwtn_2 == 1 ~ -1,
        catwtn_1 == 1 & catwtn_2 == -1 ~ 1,
        catwtn_1 == -1 & catwtn_2 == 1 ~ 1,
        catwtn_1 == -1 & catwtn_2 == -1 ~ -1,
      ),
      catbtw_2 = catbtw_1,

      cat_1 = sqrt(cat_icc_btw) * catbtw_1 + sqrt(cat_icc_wtn) * catwtn_1,
      cat_2 = sqrt(cat_icc_btw) * catbtw_2 + sqrt(con_icc_wtn) * catwtn_2,

      er_1 = rnorm(cn, mean=0, sd=1),
      er_2 = rnorm(cn, mean=0, sd=1),
      erbt_1 = rnorm(cn, mean=0, sd=1),
      erbt_2 = erbt_1,

# individual regression
# error variance
# interaction is within level. should be clarified in the manuscripts
      y_1 = beta1 * con_1 + beta2 * cat_1 + beta3 * sqrt(con_icc_wtn)* con_wtn_1*catwtn_1+ erbt_2 + er_2,
      y_2 = beta1 * con_2 + beta2 * cat_2 + beta3 * sqrt(con_icc_wtn)* con_wtn_2* catwtn_2 + erbt_2 + er_2,
    yhuman_1 = beta1 * con_1 + beta2 * cat_1 + beta3 * sqrt(con_icc_wtn)* con_wtn_1* catwtn_1 + beta3*con_btw_1*sqrt(con_icc_btw)*catwtn_1+ erbt_1 + er_1,
    yhuman_2=beta1 * con_2 + beta2 * cat_2 + beta3 * sqrt(con_icc_wtn)* con_wtn_2* catwtn_2 + beta3*con_btw_1*sqrt(con_icc_btw)*catwtn_2+ erbt_2 + er_2

    )%>%
    rename(conwtn_1 = con_wtn_1,
           conwtn_2 = con_wtn_2)
if(full){
  return(dat)
  } else if(researcher){
    dat %>%
      mutate(
      gender_1 = case_when(
        catwtn_1 == 1 ~ "male",
        catwtn_1 == -1 ~ "female"),
      gender_2 = case_when(
        catwtn_2 == 1 ~ "male",
        catwtn_2 == -1 ~ "female")) %>%
      subset(select=c(pid,y_1,y_2,
                      con_1,con_2,
                      gender_1,gender_2)) %>%
  rename(health_1 = y_1,
         health_2 = y_2,
         edu_1 = con_1,
         edu_2 = con_2) %>%
      return()
} else {
  dat %>%
    subset(select=c(pid,y_1,y_2,
                    con_1, con_2,
                    cat_1, cat_2,
                    catwtn_1, catwtn_2,
                    catbtw_1, catbtw_2,
                    conwtn_1, conwtn_2,
                    yhuman_1,yhuman_2
                    )) %>%
  return()
  }
  }
```
```{R}

dyad2ind<-function(data,
                   pid=pid){
require(tidyverse)
  dat_ind <- data %>%
    gather(key,value,-pid)%>%
    separate(key,c("key","indID"),sep="_")%>%
    spread(key,value)

  return(dat_ind)}

```
```{r}



ICC_calculator <- function(
  beta1,
  beta2,
  beta3,
  ICC,
  interaction='within',

  # if it is ratio, it is determined by the numbers you put in the within argument
  within)
{

  a<-beta1
  b<-beta2
  c<-beta3
  d<-ICC
  y<-within

  if(interaction=='within'){
  x <- (1 - d * (a^2 * y + b^2 * y + c^2 * y + 2))/((d - 1) * (a^2 + b^2))
  }
  if(interaction=='human'){
    
    x <- (1 - d*(a^2 * y + b^2 * y + c^2* y + 2))/((d - 1) * (a^2 + b^2 + c^2))
  }

 return(x)
}



```

# test human interaction 
```{r}
ICC_calculator(beta1=0.3, beta2=0.1, beta3=0.1, ICC=0.2,within=100, interaction='human')
#18.18182

nrep <- 100
sim_result <- vector ("list", length = nrep)
icc <- vector("list", length=nrep)


 for (i in  seq_len(nrep)) {
   # run a null model
  sim_data<-gen_dyadic(cn=510,
                               con_icc_wtn = 100,
                                con_icc_btw = 18.18182,
                                cat_icc_wtn = 100,
                              cat_icc_btw = 18.18182,
                               beta1=0.3,
                               beta2=0.1,
                               beta3=0.1,
                               )
   sim_data<-dyad2ind(sim_data)
   null<-lmer(yhuman ~ 1 + (1|pid)z)
  sim_result[[k]] <- jtools::summ(null) # put nicer output in the list
   icc[[k]]<-unlist(sim_result[[k]][3])[3] #extract ICC

  }
   df <- data.frame(matrix(unlist(icc), nrow=length(icc), byrow=TRUE))
  colnames(df) <- c('icc')
  df$icc2 <-as.numeric(df$icc)
  # mean of these icc CHECK
  meanICC <- mean(df$icc2)

  conditions$real_ICC[i] <- meanICC
}

```
